%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.93]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titrule]
% Clean balanced spacing: 10pt before a section rule, 5pt after, to look perfectly readable and professional
\titlespacing{\section}{0pt}{10pt}{5pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%for social icons
\usepackage{fontawesome5}

% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \vspace{-4pt}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Vishal Rawal} \\[6pt]
\href{https://github.com/vishallrawal}{\raisebox{-0.05\height}\faGithub\ vishallrawal} \ $|$ \ 
\href{https://linkedin.com/in/vishalrawal}{\raisebox{-0.05\height}\faLinkedin\ vishallrawal} \ $|$ \ 
\href{https://vishallrawal.github.io/portfolio/}{\raisebox{-0.05\height}\faGlobe \ vishallrawal.github.io/portfolio} \ $|$ \ 
\href{mailto:vishalrawal448@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vishalrawal448@gmail.com} \ $|$ \ 
\href{tel:+918128073844}{\raisebox{-0.05\height}\faMobile \ +91-8128073844} \\
\small{Surat, Gujarat, India}
\end{tabularx}
\vspace{2pt}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Detail-oriented Frontend Developer and BCA student at SDJ International College with a strong foundation in modern web architectures (React, Astro, TypeScript, Tailwind CSS). Experienced in building responsive, interactive applications, integrating generative AI SDKs, and managing local database transactions. Passionate about problem-solving and open-source contributions. Seeking a Frontend Developer Internship to deliver premium user experiences.

%----------------------------------------------------------------------------------------
% OPEN SOURCE CONTRIBUTIONS
%----------------------------------------------------------------------------------------
\section{Open Source Contributions}

\begin{joblong}{Independent Contributor}{2024 - Present}
\item Staged, reviewed, and pushed bug fixes and documentation enhancements to public GitHub projects.
\item Collaborated with maintainers on codebase improvements, issue resolution, and Git pull request reviews.
\end{joblong}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Featured Frontend Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{VidyaEnroll -- AI Admission Portal} & \hfill \href{https://vishallrawal.github.io/vidhyaenroll-admission-system/}{Live Demo} \ $|$ \ \href{https://github.com/vishallrawal/vidhyaenroll-admission-system}{GitHub} \\[2pt]
\multicolumn{2}{@{}X@{}}{\small{Developed a responsive multi-step admission wizard using React, TypeScript, and Bootstrap 5. Features real-time subject eligibility evaluations, Aadhaar validation rules, and a mock payment portal with 3D-tilting credit card effects and UPI QR scanning simulator. Connected to Gemini AI API for counseling query dialogue responses.}}  \\[6.5pt]

\textbf{FlixCart -- Online E-Commerce Catalog} & \hfill \href{https://vishallrawal.github.io/FlixCart-Website/}{Live Demo} \ $|$ \ \href{https://github.com/vishallrawal/FlixCart-Website}{GitHub} \\[2pt]
\multicolumn{2}{@{}X@{}}{\small{Built a responsive Astro and React catalog featuring Zustand client-side shopping list state management, categories autocomplete searches, product comparisons, and dark/light mode toggles styled using Tailwind CSS utility variables.}}  \\[6.5pt]

\textbf{Personal Portfolio Website} & \hfill \href{https://vishallrawal.github.io/portfolio/}{Live Demo} \ $|$ \ \href{https://github.com/vishallrawal/portfolio}{GitHub} \\[2pt]
\multicolumn{2}{@{}X@{}}{\small{Designed a premium, state-of-the-art developer showcase featuring a dynamic dark theme, glassmorphic layout, and glowing gradients. Integrated an interactive skills marquee, a contact validation system, and a custom blog layout.}}  \\[6.5pt]

\textbf{Movie Booking \& Showcase Website} & \hfill \href{https://github.com/vishallrawal/movie-website}{GitHub} \\[2pt]
\multicolumn{2}{@{}X@{}}{\small{Engineered a responsive movie ticketing application containing interactive seat selection matrices, pricing schedules, and transaction receipts. Styled using HTML5, CSS3, Bootstrap, and vanilla JavaScript.}}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}	
2024 - 2027 & Bachelor of Computer Applications (BCA) at \textbf{SDJ International College} & (CGPA: 8.6/10.0) \\
 & Veer Narmad South Gujarat University, Surat, Gujarat & \\
\end{tabularx}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages & JavaScript (ES6+), TypeScript, HTML5, CSS3, C, Python \\
Frameworks \& Libs & React.js, Astro, Tailwind CSS, Bootstrap 5, Node.js, Express.js, Django \\
Databases & MongoDB, MySQL, SQLite \\
Developer Tools & Git, GitHub, VS Code, Vite, npm / bun, Figma \\
Core Concepts & REST APIs, Responsive Design, State Management, OOP, Data Structures, AI APIs Integration
\end{tabularx}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements \& Extra-Curriculars}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Blind Coding & Winner of inter-college coding competition. \\
Error Finding & Winner of error detection and debugging competition. \\
Extra-Curricular & Active contributor to college technical magazine; volunteer at student workshops.
\end{tabularx}

\end{document}
